\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-09 main.tex
Updates from Overleaf

\newenvironment{code}{\captionsetup{type=listing}}{\hfill}
\SetupFloatingEnvironment{listing}{name=Code Block}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
from superscreen import Parameter

@@

param = Parameter(f, a=0, b=1)
print(param) # Parameter<f(a=0, b=1)>
other_param = Parameter(f, a=2, b=3)
print(other_param) # Parameter<f(a=2, b=3)>
print(param(0, 0) == f(0, 0, a=0, b=1)) # True
print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
param_squared = param ** 2
print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
) # True
\end{minted}
\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
\label{code:parameters}
\end{code}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
import superscreen.geometry as geo

def make_ring(
    inner_radius: float = 2.5,
    outer_radius: float = 5.0,
    inner_points: int = 300,
    outer_points: int = 500,
    Lambda: float = 1.0,
    square: bool = False,
) -> sc.Device:
    """Creates a Device representing a circular or square ring."""
    if square:
        outer = geo.square(2 * outer_radius, points_per_side=outer_points // 4)
        inner = geo.square(2 * inner_radius, points_per_side=inner_points // 4)
        bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
    else:
        outer = geo.circle(outer_radius, points=outer_points)
        inner = geo.circle(inner_radius, points=inner_points)
        bbox = geo.circle(1.4 * outer_radius, points=50)
    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer)]
    holes = [sc.Polygon("hole", layer="base", points=inner)]
    abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
    return sc.Device(
        "ring",
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units="um",
    )
\end{minted}
\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\end{code}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
import matplotlib.pyplot as plt

fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
\label{code:mesh_generation}
\end{code}

@@

% \begin{code}
% \begin{minted}[fontsize=\small]{python}
% import numpy as np

@@

% # Specify a sequence of (x, y) coordinates to plot cross-sections
% # of the simulated currents and fields.
% xs = np.linspace(-5.5, 5.5, 201) # [microns]
% cross_sections = [ # Two sets of [x, y] coordinates
%     np.stack([xs, xs], axis=1), # diagonal cross-section
%     np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
% ]
% for solution in (uniform_field_solution, trapped_flux_solution):
%     solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
%     solution.plot_fields(cross_section_coords=cross_sections)
% \end{minted}
% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
% \label{code:ring_circulating_current}
% \end{code}

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Figure~\ref{fig:square-ring-results} and Section~\ref{section:overview:visualization}).

@@

See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    length_units="um",
)
device.make_mesh(min_triangles=8_000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 2, 5) # [device.length_units]
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(device=device, vortices=vortices)[-1]
    # Use solution.field_at_position() to evaluate the magnetic field profile,
    # and Solution.polygon_fluxoid() to calculate fluxoids.
\end{minted}
\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
\label{code:pearl-vortex}
\end{code}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\mu\mathrm{m}$ as a function of the film's effective penetration depth, $\Lambda$. (a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (b) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$. (c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film. (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (c). (e) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (f) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (e). In (c) and (e), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. }
    \label{fig:pearl}
\end{figure}

@@

\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}). We calculate the ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$. We calculate the ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule. The sum of these two terms gives the fluxoid $\Phi^f_S$. See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all
# other inputs to superscreen.solve_many() into a dictionary
# called other_kwargs.

@@

# Start a ray cluster
ray.init(num_cpus=num_cpus)
# Solve the models
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
# Shutdown the ray cluster
ray.shutdown()
\end{minted}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API. See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
\label{code:ray-python}
\end{code}

\begin{minipage}{\textwidth}
\begin{code}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num-cpus=3
\end{minted}

@@

\begin{minted}[fontsize=\small]{bash}
# Shut down the ray cluster from the command line
ray stop
\end{minted}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface. See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
\label{code:ray-cli}
\end{code}
\end{minipage}

>>>>

\newenvironment{code}{\captionsetup{type=listing}}{\hfill}
\SetupFloatingEnvironment{listing}{name=Code Block}
\BeforeBeginEnvironment{code}{\begin{minipage}{\textwidth}}
\AfterEndEnvironment{code}{\end{minipage}}
\captionsetup[listing]{skip=0pt}

@@

\begin{code}
\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
\label{code:parameters}
\begin{minted}[fontsize=\small]{python}
from superscreen import Parameter

@@

param = Parameter(f, a=0, b=1)
print(param) # Parameter<f(a=0, b=1)>
other_param = Parameter(f, a=2, b=3)
print(other_param) # Parameter<f(a=2, b=3)>
print(param(0, 0) == f(0, 0, a=0, b=1)) # True
print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
param_squared = param ** 2
print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
) # True
\end{minted}
\end{code}

@@

\begin{code}
\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
import superscreen.geometry as geo

def make_ring(
    inner_radius: float = 2.5,
    outer_radius: float = 5.0,
    inner_points: int = 300,
    outer_points: int = 500,
    Lambda: float = 1.0,
    square: bool = False,
) -> sc.Device:
    """Creates a Device representing a circular or square ring."""
    if square:
        outer = geo.square(2 * outer_radius, points_per_side=outer_points // 4)
        inner = geo.square(2 * inner_radius, points_per_side=inner_points // 4)
        bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
    else:
        outer = geo.circle(outer_radius, points=outer_points)
        inner = geo.circle(inner_radius, points=inner_points)
        bbox = geo.circle(1.4 * outer_radius, points=50)
    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer)]
    holes = [sc.Polygon("hole", layer="base", points=inner)]
    abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
    return sc.Device(
        "ring",
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units="um",
    )
\end{minted}
\end{code}

@@

\begin{code}
\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
\label{code:mesh_generation}
\begin{minted}[fontsize=\small]{python}
import matplotlib.pyplot as plt

fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\end{code}

@@

% \begin{code}
% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
% \label{code:ring_circulating_current}
% \begin{minted}[fontsize=\small]{python}
% import numpy as np

@@

% # Specify a sequence of (x, y) coordinates to plot cross-sections
% # of the simulated currents and fields.
% xs = np.linspace(-5.5, 5.5, 201) # [microns]
% cross_sections = [ # Two sets of [x, y] coordinates
%     np.stack([xs, xs], axis=1), # diagonal cross-section
%     np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
% ]
% for solution in (uniform_field_solution, trapped_flux_solution):
%     solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
%     solution.plot_fields(cross_section_coords=cross_sections)
% \end{minted}
% \end{code}

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).

@@

% See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()} (see Code Block~\ref{code:pearl-vortex}). A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

\begin{code}
\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
\label{code:pearl-vortex}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    length_units="um",
)
device.make_mesh(min_triangles=8_000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 2, 5) # [device.length_units]
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(device=device, vortices=vortices)[-1]
    # Use solution.field_at_position() to evaluate the magnetic field profile,
    # and Solution.polygon_fluxoid() to calculate fluxoids.
\end{minted}
\end{code}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\mu\mathrm{m}$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure}

@@

\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}). The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$. The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule. The sum of these two terms gives the fluxoid $\Phi^f_S$.

Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\mu\mathrm{m}$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
% See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.

@@

\begin{code}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API. See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
\label{code:ray-python}
\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all
# other inputs to superscreen.solve_many() into a dictionary
# called other_kwargs.

@@

# Start a ray cluster
ray.init(num_cpus=num_cpus)
# Solve the models
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
# Shutdown the ray cluster
ray.shutdown()
\end{minted}
\end{code}

\begin{minipage}{\textwidth}
\begin{code}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface. See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
\label{code:ray-cli}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num-cpus=3
\end{minted}

@@

\begin{minted}[fontsize=\small]{bash}
# Shut down the ray cluster from the command line
ray stop
\end{minted}
\end{code}
\end{minipage}
